The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2022-11-11 paper.tex

\begin{acknowledgments}
  TODO
\end{acknowledgments}

@@

Data sharing is not applicable to this article as no new data were created or analyzed in this study.

>>>>

\section*{Supplementary Material}

Full set of line-count data and script used to produce Figure \ref{fig:histogram}.

\begin{acknowledgments}

The authors would like to thank all \yaq{} users and contributors.
We would also like to acknowledge the developers of the broader open source software community upon-which this project rests.

This work was supported by the National Science Foundation under grant CHE-1709060.

\end{acknowledgments}

@@

The data that supports the findings of this study are available within the supplementary material.
